\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-15 paper/examples.tex
paper: add query plan trees

>>>>

\begin{figure}
  \Tree
  [.$\pi_{\text{income, AVG(white\_blood\_cell\_ct)}}$
    [.$g_{\text{income, AVG(white\_blood\_cell\_ct)}}$
      [.$\mu_{\text{demo.income}}$
        [.$\bowtie_{\text{exams.id} = \text{demo.id}}$
          [.$\mu_{\text{labs.white\_blood\_cell\_ct}}$
            [.$\bowtie_{\text{exams.id} = \text{labs.id}}$
              [.$\sigma_{\text{exams.weight} \geq 120}$ 
                [.$\mu_{\text{exams.weight}}$ exams ] 
              ] 
              labs 
            ]
          ]
        [.$\sigma_{\text{demo.gender} = 2}$ demo ]
      ] 
    ] 
  ] 
]
\caption{A plan for the query in Fig.~\ref{fig:example-query}, optimized for quality.}
\label{fig:quality-plan}
\end{figure}

\begin{figure}
  \Tree
  [.$\pi_{\text{income, AVG(white\_blood\_cell\_ct)}}$
    [.$g_{\text{income, AVG(white\_blood\_cell\_ct)}}$
      [.$\delta_{\text{demo.income, labs.white\_blood\_cell\_ct}}$
        [.$\bowtie_{\text{exams.id} = \text{labs.id}}$
          [.$\bowtie_{\text{demo.id} = \text{exams.id}}$
            [.$\sigma_{\text{demo.gender} = 2}$ demo ]
            [.$\sigma_{\text{exams.weight} \geq 120}$ [.$\mu_{\text{exams.weight}}$ exams ] ] ] labs ] ] ] ]
\caption{A plan for the query in Fig.~\ref{fig:example-query}, optimized for performance.}
\label{fig:fast-plan}
\end{figure}

First, consider the plan in Fig.~\ref{fig:fast-plan}.
This plan will be generated for the query in Fig.~\ref{example-query} when the optimizer is requested to produce the fastest possible plan, without considering the accuracy penalty.
There are several features of this query plan that highlight the subtleties of optimizing queries which contain imputation operators.
First, this plan will drop tuples which contain null values, rather than
